---
title: "Simple document"
author: "Hyun Jin Jung"
date: "2023-9-12"
output:
  github_document
---

```{r, echo = FALSE, message = FALSE}
library(tidyverse)
```

I'm an R Markdown document! 

# Section 1: First code chunk

Here's a **code chunk** that samples from 
a _normal distribution_:

```{r}
samp = rnorm(100)
length(samp)
```

# Section 2: Make a plot

This code is borrowed from last lecture; it creates a dataframe for plotting.

```{r}
set.seed(1)

plot_df = 
  tibble(
  x = rnorm(1000, sd = .5),
  y = 1 + 2 * x + rnorm(1000)
)
```

Next up is a histogram of the 'x' variable in 'plot_df'

```{r}
ggplot(plot_df, aes(x = x)) + geom_histogram()
```

Lastly, I'll do a scatterplot.

```{r}
ggplot(plot_df, aes(x = x, y = y)) + geom_point()
```


# Section 3: Learning assessment!

The chunk below creates a dataframe containing a sample of size 500 from a 
random normal variable, constructs the specified logical vector, takes the 
absolute value of each element of that sample,and produces a histogram of 
the absolute value. The code chunk also finds the median of the sample and
stores it for easy in-line printing.

```{r la_df}
library(tidyverse)

la_df = tibble(
  num_samp = rnorm(500, mean = 1),
  log_vec = num_samp > 0,
  abs_val = abs(num_samp)
)

ggplot(la_df, aes(x = abs_val)) + geom_histogram()

median_samp = median(pull(la_df, num_samp))
```

The median of the variable containing absolute values is 
`r round(median_samp, digits = 2)`.





